Financialisation of Commodity Markets

### 2024-11-19 docs/paper.qmd
Refactor correlations analysis
to accommodate for cross-correlation analysis

make_table("correlations - periods", c("country", "sector", "subsector"), colnames, align, 1L:8L, 5L:8L)
```

@@

make_table("correlations - years", c("country", "sector", "subsector"), colnames, align, 1L:14L, 5L:14L) %>%
  landscape()
```

>>>>

make_table("correlations - inner - periods", c("country", "sector", "subsector"), colnames, align, 1L:8L, 5L:8L)
```

@@

make_table("correlations - inner - years", c("country", "sector", "subsector"), colnames, align, 1L:14L, 5L:14L) %>%
  landscape()
```
